### 2017-05-03 introduction.tex
Add files via upload

The following two chapters address questions one and two respectively. Chapter \ref{paper1} details and evaluates a method to retrieve atmospherically corrected, hemispherical urban T\textsubscript{surf} from time-continuous measurements of upwelling longwave radiation. Chapter \ref{paper2} explores the temporal and geometric nature of sUHI through an eight month climatological analysis of hemispherical sUHI and compares sUHI magnitudes from several representations of the urban surface.

>>>>

The following two chapters address questions one and two respectively. Chapter \ref{paper1} details and evaluates a method to retrieve atmospherically corrected, hemispherical urban T\textsubscript{surf} from time-continuous measurements of upwelling longwave radiation. Chapter \ref{paper2} explores the temporal and geometric nature of sUHI through long-term climatological analysis of hemispherical sUHI and compares sUHI magnitudes from several representations of the urban surface.

### 2017-05-03 paper1.tex
Add files via upload

To save computational time and facilitate broader use of the method, a parameterization scheme was developed to simplify the correction process. In the parameterization, a suite of radiative transfer simulations is run prior to correction (as opposed to at each time step) to retrieve $\tau$ for a range of humidities and path lengths. T\textsubscript{surf} and T\textsubscript{air} are held constant in these simulations as they have a relatively small effect on $\tau$. Simulations for path lengths from 1 to 100 \si{\meter} and water vapor mass densities from 0.1 to 23.5 \si{\gram\per\meter\cubed} are included in Appendix \ref{appendixa}. Sensor-surface geometry is approximated as a single view factor weighted, azimuthally averaged surface-sensor path length calculated using the surface-sensor-sun urban model \citep{Soux2004} and a simplified DBM. This path length represents the average distance from the sensor to the surface as "seen" by the sensor. For each time step, measured humidity is used to infer a hemispherical transmittance ($\overline{\tau_{\Phi}}$) for the approximated surface-sensor geometry. A parameterized T\textsubscript{hem, r} can then be calculated by using measured (in this case, profile averaged) T\textsubscript{air} to decompose measured L\textsubscript{up} into irradiance received by the sensor from the surface $L_{surf}^{at-sensor}$ and from the atmosphere $L_{atm}^{at-sensor}$ via,

@@

Using this parameterization, a climatology of T\textsubscript{hem, para} for a given surface geometry can be retrieved from approximately 100 simulations as opposed to the many millions needed for full hemispherical radiative transfer simulation. A variety of online and offline, open and closed source resources are available for radiative transfer simulation \citep{Gastellu-Etchegorry1996,Berk1987,Buehler2005}, some of which are available for free or at a low cost (Spectral-Calc), all of which are likely to provide similar results to those included in Appendix \ref{appendixa}.

>>>>

To save computational time and facilitate broader use of the method, a parameterization scheme was developed to simplify the correction process. In the parameterization, a suite of radiative transfer simulations is run prior to correction (as opposed to at each time step) to retrieve $\tau$ for a range of humidities and path lengths. T\textsubscript{surf} and T\textsubscript{air} are held constant in these simulations as they have a relatively small effect on $\tau$. Simulations for path lengths from 1 to 100 \si{\meter} and water vapor mass densities from 0.1 to 23.5 \si{\gram\per\meter\cubed} are included in Appendix \ref{appendixa}. Sensor-surface geometry is approximated as a single view factor weighted, azimuthally averaged, surface-to-sensor path length calculated using the surface-sensor-sun urban model \citep{Soux2004} and a simplified DBM. This path length represents the average distance from the sensor to the surface as "seen" by the sensor. For each time step, measured humidity is used to infer a hemispherical transmittance ($\overline{\tau_{\Phi}}$) for the approximated surface-sensor geometry. A parameterized T\textsubscript{hem, r} (T\textsubscript{hem, para}) can then be calculated by using measured (in this case, profile averaged) T\textsubscript{air} to decompose measured L\textsubscript{up} into irradiance received by the sensor from the surface $L_{surf}^{at-sensor}$ and from the atmosphere $L_{atm}^{at-sensor}$ via,

@@

Using this parameterization, a climatology of T\textsubscript{hem, para} for a given surface geometry can be retrieved from approximately 100 simulations as opposed to the many thousands needed for full hemispherical radiative transfer simulation. A variety of online and offline, open and closed source resources are available for radiative transfer simulation \citep{Gastellu-Etchegorry1996,Berk1987,Buehler2005}, some of which are available for free or at a low cost (Spectral-Calc), all of which are likely to provide similar transmittances to those included in Appendix \ref{appendixa}. Figure \ref{para_eval} and Table \ref{parastats} summarize parameterization performance relative to corrected T\textsubscript{hem, r}. Errors are largest during the daytime hours (shaded in grey), where the profile averaged T\textsubscript{air} overestimates above canyon T\textsubscript{air} and underestimates near-surface T\textsubscript{air}. Neutral stability in the nighttime and early morning hours reduces these errors significantly as the canyon T\textsubscript{air} profile is approximately isothermal.
